Questioning how Researchers Develop and Present Intrusion Detection Systems

### 2014-09-21 docs/questioning.tex
adding content, filling the tables.

We decided to narrow down our
research to countermeasures developed to
detect attacks that target applications. Such attacks include
buffer overflow attacks~\cite{K11}, {\sc sql} injection
attacks~\cite{RL12b}, cross-site scripting ({\sc xss})
attacks~\cite{SG07}, cross-site request forgery ({\sc csrf})
attacks~\cite{LZRL09} and others.
Such attacks top the vulnerability lists of numerous bulletin providers for several
years.\footnote{\url{http://www.sans.org/top-cyber-security-risks/}, \url{http://cwe.mitre.org/top25/}}
Consider the {\sc owasp}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
(Open Web Application Security Project)
Top Ten project whose main goal is to raise awareness about
web application security by identifying some of the most critical risks facing
organizations which is referenced by numerous researchers.
In its three consecutive Top Ten lists (2007, 2010, 2013), different
source code-driven injection attacks dominate the top five positions.
This indicates that
apart from the fact that malicious users find new ways to bypass
defense mechanisms by using a variety of techniques despite the numerous
countermeasures that are being introduced.
Note that the number of systems developed to counter {\sc sql}
injection attacks until 2006 was more than twenty~\cite{HVO06}.
Since then the number has doubled.
In our research we focus on the top {\sc tba} systems that counter
application attacks, in terms of citations.

@@

	&  	{\sc csse}~\cite{PB05} & 312 & \xmark,\xmark & 2--10\% & {\sc sql} injection \\
	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & {\bf ?},{\bf ?} & \xmark & {\sc sql} injection \\ 
	&  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
	&  	{\it Xu et al.}~\cite{XBS06} & 297 & \tick,\xmark & 76\% & {\sc sql} injection, {\sc xss} \\ 
    &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & \xmark,\xmark & 30\% & {\sc sql} injection, {\sc xss} \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & \xmark,{\bf ?} & {\bf ?} & {\sc xss} \\
	&   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & \xmark,\xmark & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & 0.09\%,\xmark & 7--17\% & {\sc xss} \\

@@

	&   {\it {\sc sql}rand}~\cite{BK04} & 286 & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} injection \\ 
	&   {\it Noncespaces}~\cite{GC09} & 109 & \tick,\tick &  10.3\% & {\sc xss} \\ 
    &   {\it x{\sc js}}~\cite{APKLM10} & 18 & \tick,\tick & 1.6--40{\it ms} & {\sc xss} \\

@@

	\multirow{13}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06} & 135 & \xmark,\xmark & 1.85\% & {\sc xss} \\ 
	&   {\it BrowserShield}~\cite{RDWDE07} & 219 & \tick,\tick & 8\% & {\sc xss} \\ 
	&   {\it CoreScript}~\cite{YCIS07} & 181 & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
	&   {\it {\sc met}}~\cite{ELX07} & 58 & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
    &   {\it {\sc beep}}~\cite{TNH07} & 282 & \tick,\tick & 14.4\% & {\sc xss} \\
    &   {\it {\sc soma}}~\cite{OWVS08} & 46 & 5,0,0,0 & 5.58\% & {\sc xss}, {\sc csrf}\\
	&   {\it Blueprint}~\cite{LV09} & 110 & \tick/\tick & 13.6\% & {\sc xss} \\ 
	&   {\it Phung et al.}~\cite{PSC09} & 75 & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
	&   {\it WebJail}~\cite{VDDPJ11} & 25 & {\bf ?},{\bf ?} & $\sim$7ms & {\sc xss} \\ 
	&   {\it ConScript}~\cite{ML10} & 122 & {\bf ?},{\bf ?} & 7\% & {\sc xss} \\
	&   {\it j{\sc csrf}}~\cite{PS11} & 2 & 2,7,0,0 & 2ms & {\sc csrf} \\
    &   {\it TreeHouse}~\cite{IW12} & 18 & {\bf ?},{\bf ?} & 757–-1218ms & {\sc xss} \\
   	&   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & {\bf ?},{\bf ?} & up to 365\% & {\sc xss}\\

@@

    &   {\it {\sc didafit}}~\cite{LLW02} & 85 & \xmark,\xmark & {\bf ?} & {\sc sql} injection \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & \tick,\tick & {\bf ?} & {\sc sql} injection \\ 
	&   {\it Valeur et al.}~\cite{VMV05} & 226 & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} injection \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & {\bf ?},{\bf ?} & 3\% & {\sc sql} injection \\

@@

\begin{table*}
\centering
    \begin{threeparttable}
    \begin{small}
\scalebox{0.99}{
    \begin{tabular}{l|c|ccc}
    \hline
    \bf{Approach}
	& \bf{Mechanism}
    & \multicolumn{3}{|c|}{Availability} \\
	&& \bf{Source Code}
	& \bf{Executable}
	& \bf{Testbed} \\
    \hline
	\multirow{9}{*}{Runtime Tainting}
	&  	{\sc csse}~\cite{PB05} & - & - & - \\
	&  	{\it Haldar et al.}~\cite{HCF05}  & - & - & - \\ 
	&  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
	&  	{\it Xu et al.}~\cite{XBS06}  & - & - & - \\
    &  	{\it {\sc wasc}}~\cite{NLC07} & - & - & - \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & - & - & - \\
	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & - & - & - \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & - & - & - \\
	& 	{\it Stock et al.}~\cite{SLMS14} & - & - & - \\
	\hline
	\hline      
	\multirow{3}{*}{{\sc isr}}
	&   {\it {\sc sql}rand}~\cite{BK04} & - & - & - \\
	&   {\it Noncespaces}~\cite{GC09} & - & - & - \\ 
    &   {\it x{\sc js}}~\cite{APKLM10} & - & - & - \\
	\hline
	\hline    
	\multirow{13}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06} & - & - & - \\ 
	&   {\it BrowserShield}~\cite{RDWDE07} & - & - & - \\
	&   {\it CoreScript}~\cite{YCIS07} & - & - & - \\
	&   {\it {\sc met}}~\cite{ELX07} & - & - & - \\ 
    &   {\it {\sc beep}}~\cite{TNH07} & - & - & - \\
    &   {\it {\sc soma}}~\cite{OWVS08} & - & - & - \\
	&   {\it Blueprint}~\cite{LV09} & - & - & - \\
	&   {\it Phung et al.}~\cite{PSC09} & - & - & - \\
	&   {\it WebJail}~\cite{VDDPJ11} & - & - & - \\
	&   {\it ConScript}~\cite{ML10} & - & - & - \\
	&   {\it j{\sc csrf}}~\cite{PS11} & - & - & - \\
    &   {\it TreeHouse}~\cite{IW12} & - & - & - \\
   	&   {\it {\sc js}and}~\cite{AVBPDP12} & - & - & - \\
	\hline
	\hline  
        \multirow{12}{*}{Training}
    &   {\it {\sc didafit}}~\cite{LLW02} & - & - & - \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & - & - & - \\ 
	&   {\it Valeur et al.}~\cite{VMV05} & - & - & - \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & - & - & - \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & - & - & - \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & - & - & - \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & - & - & - \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & - & - & - \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & - & - & - \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & - & - & - \\
	& 	{\it Diglossia}~\cite{SMS13} & - & - & - \\
	\hline
    \end{tabular}}
    \caption{Availability of the corresponding mechanisms.}
    \label{tab:comp2}
    \end{small}
    \end{threeparttable}
\end{table*}

>>>>

We decided to narrow down our
research to countermeasures developed to
detect attacks that target applications. Such attacks include
buffer overflow attacks~\cite{K11}, {\sc sql} injection
attacks~\cite{RL12b}, cross-site scripting ({\sc xss})
attacks~\cite{SG07}, cross-site request forgery ({\sc csrf})
attacks~\cite{LZRL09} and others.
Such attacks top the vulnerability lists of numerous bulletin providers for several
years.\footnote{\url{http://www.sans.org/top-cyber-security-risks/}, \url{http://cwe.mitre.org/top25/}}
Consider the {\sc owasp}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
(Open Web Application Security Project)
Top Ten project whose main goal is to raise awareness about
web application security by identifying some of the most critical risks facing
organizations which is referenced by numerous researchers.
In its three consecutive Top Ten lists (2007, 2010, 2013), different
source code-driven injection attacks dominate the top five positions.
This indicates that
apart from the fact that malicious users find new ways to bypass
defense mechanisms by using a variety of techniques despite the numerous
countermeasures that are being introduced.
Note that the number of systems developed to counter {\sc sql}
injection attacks until 2006 was more than twenty~\cite{HVO06}.
Since then the number has doubled.
In our research we focus on the top {\sc tba} systems that counter
application attacks, in terms of citations.
% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.

@@

	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection \\
	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
	% &  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% & {\sc sql} injection, {\sc xss}, Buffer Overflows \\ 
    &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% & {\sc sql} injection, {\sc xss} \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} & {\sc xss} \\
	&   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (15,{\sc nq},{\sc nq},{\sc nq})\_r & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% & {\sc dom}-based {\sc xss} \\

@@

	&   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & +6.5{\it ms} & {\sc sql} injection \\ 
	&   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
    &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} & {\sc xss} \\

@@

	\multirow{12}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
	&   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
	&   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\ 
	&   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
    &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% & {\sc xss} \\
    &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf}\\
	&   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\ 
	&   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
	&   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\ 
	&   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
	&   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
    &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
   	% &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
   	% TODO@dimitro: discuss this with Panos?

@@

    &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\bf ?} & {\sc sql} injection \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,0,0,0)\_a & {\bf ?} & {\sc sql} injection \\ 
	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} & {\sc sql} injection \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\

@@

\section{Analysis}

{\sc na} means that a requirement is not even mentioned in the paper.
{\sc nq} indicates that a requirement is mentioned in the publication
but it is not quantified.

Notes on taint tools:
\begin{enumerate}
\item The accuracy testing of {\sc csse}~\cite{PB05} was based on 
defects found in the security mailing
list: {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}.
\item During their evaluation, the authors of~\cite{HCF05} have only performed
two attacks in one synthetic benchmark ({\sc owasp}'s
{\it WebGoat}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_WebGoat_Project}}).
\item The testing in~\cite{XBS06} was made based on
defects with specific {\sc cve id}s.
\item The authors of {\it {\sc wasc}}~\cite{NLC07}
mention the vulnerabilities (specific {\sc cve id}s)
exploited and the corresponding applications but they do not explicitly
state how many attacks they launched (``{\it [...] launched a variety of
attacks against it}").
\item The authors of~\cite{VFJKKV07} do the same.
However, even if they do not mention specific {\sc cve id}s,
they browsed applications without performing attacks.
\item Even if the authors of {\it Noxes}~\cite{KKVJ06,KJKV09} state in
both papers that ``{\it [...] we are planning to make the tool available as
a freeware utility}." the tool cannot be found anywhere on the Internet.
The vulnerabilities exploited during testing were reported
by {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}.
\item {\it {\sc php} Aspis}~\cite{PMP11} was tested on only one
application (Wordpress 2.9.2) with multiple vulnerabilities (specific {\sc cve id}s).
\item During their initial tests, the authors of
managed to bypass the browser-based {\sc xss} filters of the
73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
Then they proposed an approach that detected all the attacks they
found (1169). This is a complex paper --- we need to elaborate.
\end{enumerate}

Notes on {\sc isr} mechanisms:
\begin{enumerate}
\item {\it {\sc sql}rand}~\cite{BK04}: Both exploits from {\sc cve}.
\item {\it Noncespaces}~\cite{GC09} was only tested on one
known vulnerable application (TikiWiki). The authors mention that they performed
a number of attacks but they do not state how many.
\item The authors of {\it x{\sc js}}~\cite{APKLM10}, have tested
their mechanisms based on real-world attacks coming from
{\sc xss}ed.com.\footnote{www.xssed.com}
\end{enumerate}

Notes on policy enforcement tools:
\begin{enumerate}
\item Just like the authors of {\it x{\sc js}~\cite{APKLM10},
the authors of {\sc dsi}}~\cite{NSS06}, have tested
their mechanisms based on real-world attacks coming from
{\sc xss}ed.com.\footnote{www.xssed.com}
\item The testing of {\it BrowserShield}~\cite{RDWDE07}
involved {\sc xss} vulnerabilities reported by Microsoft
in 2005.\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
The link currently shows defects for 2014.
\item {\it CoreScript}~\cite{YCIS07} is more of a programming
language\footnote{``[...] uses program instrumentation for
JavaScript where untrusted JavaScript
code goes through a rewriting process according to a security policy
before executing them in the browser"~\cite{PSC09}.}
than an {\sc IDS}.
\item Surprisingly, {\sc met}~\cite{ELX07} was not tested at all.
\item {\sc beep}~\cite{TNH07}'s test suite was based on 61 {\sc xss}
attack vectors published by \url{ha.ckers.org}.
\item {\sc soma}~\cite{OWVS08} --- all synthetics.
\item The attacks used for the testing of {\it Blueprint}~\cite{LV09},
came from \url{ha.ckers.org}.
\item {\it Phung et al.}~\cite{PSC09} also utilized \url{ha.ckers.org}.
\item {\it WebJail}~\cite{VDDPJ11} --- not tested at all.
\item {\it ConScript}~\cite{ML10} --- not tested at all. A scheme
similar to {\it CoreScript}~\cite{YCIS07}.
\item {\it j{\sc csrf}}~\cite{PS11} --- based on {\sc csrf}
defects with specific {\sc cve id}s.
\item The authors of {\it TreeHouse}~\cite{IW12} have tested
only the overhead and how easy is to incorporate the mechanism
into an application.
\end{enumerate}

Notes on training-based mechanisms:
\begin{enumerate}
\item {\it {\sc didafit}}~\cite{LLW02} is one of
the first {\sc ids}.
\item {\sc amnesia}~\cite{HO05,HO06,HO05b} was tested
on applications with known vulnerabilities taken
from \url{http://gotocode.com} plus two synthetic benchmarks.
Interestingly, in one of the papers~\cite{HO06},
the authors mention that the tool can produce both {\sc fp} and
{\sc fn}.
\item {\it libAnomaly}~\cite{VMV05} --- one application tested ({\sc php}-Nuke).
\item {\sc sqlg}uard~\cite{BWS05} --- no testing at all.
\end{enumerate}

\begin{table*}
\centering
    \begin{threeparttable}
    \begin{small}
\scalebox{0.99}{
    \begin{tabular}{l|c|ccc}
    \hline
    \bf{Approach}
	& \bf{Mechanism}
    & \multicolumn{3}{|c|}{Availability\tnote{1}} \\
	&& \bf{Source Code}
	& \bf{Executable}
	& \bf{Testbed} \\
    \hline
	\multirow{9}{*}{Runtime Tainting}
	&  	{\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
	% &  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
	&  	{\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
    &  	{\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\sc ao} & {\sc na} & {\sc ao} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline      
	\multirow{3}{*}{{\sc isr}}
	&   {\it {\sc sql}rand}~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Noncespaces}~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it x{\sc js}}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline    
	\multirow{12}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it CoreScript}~\cite{YCIS07} & {\sc ao} & {\sc na} & {\sc na} \\
	&   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
    &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
	&   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
	&   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it ConScript}~\cite{ML10} & {\sc ao} & {\sc na} & {\sc na} \\
	&   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
    &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
   	% &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
	\hline
	\hline  
        \multirow{12}{*}{Training}
    &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\sc ao} & {\sc na} \\
	&   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & - & - & - \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & - & - & - \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & - & - & - \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & - & - & - \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & - & - & - \\
	& 	{\it Diglossia}~\cite{SMS13} & - & - & - \\
	\hline
    \end{tabular}}
        \begin{tablenotes}
	\begin{footnotesize}
       \item[1] The check mark (\tick) indicates that some point within
       the publication there is a homepage where the reader can refer to, to
       download the corresponding software. {\sc ao} (Available On-line) suggests
       that the software is available on-line but the
       address was not mentioned in the paper, which probably indicates that
       the authors made it available after the publication. The question ({\bf ?})
       mark, indicates that the a homepage for the software was included
       in the publication but now it is not available.
	\end{footnotesize}
    \end{tablenotes}
    \caption{Availability of the corresponding mechanisms.}
    \label{tab:comp2}
    \end{small}
    \end{threeparttable}
\end{table*}
